---
title: "HR Rates"
author: "Jon Phillips"
date: '2022-05-08'
output: html_document
---

#### The Data?

All of the data is contained as data frames within the Lahman package.

#### Packages

dplyr, ggplot2, Lahman

```{r}
library(dplyr)
library(ggplot2)
library(Lahman)
```

#### Season Home Run Rates

Overall Home Run rates since 1960. From the Teams data frame, first we'll filter by yearID and then group by yearID.  Summarize the data by HR, Strikeouts, and At Bat.  The calculation for HR rate is HR / (AB - SO).

```{r}
Teams %>% 
  filter(yearID >= 1960) %>% 
  group_by(yearID) %>% 
  summarize(HR = sum(HR),
            AB = sum(AB),
            SO = sum(SO),
            Rate = HR / (AB - SO)) -> HR
head(HR)
```

#### Graphing Home Run Rates

Using ggplot2, yearID on the x-axis and Rate on the y-axis. Using geom_smooth to graph a line (lowess) to see the trend.
```{r}
ggplot(HR, aes(yearID, Rate)) +
  geom_point() +
  geom_smooth(span = 0.2) +
  labs(title = "Overall HR Rate since 1960")
```
